Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-07-31 tex/scam/appendix.tex
results update

\begin{theorem}
\label{thm:convex_consistent}
Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq c sB \sqrt{ \frac{1}{n} \log^2 np}$.

Then, with probability at least $1-\delta$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
\end{align}

@@

The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4B$ because $f^*_k$ as is $L$-Lipschitz and supported on $[-b, b]$.

@@

By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_2(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.

By Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h^U, h^L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$.

@@

$$
\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}
$$.

We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. 
Therefore,  
\[
|\langle w, h - h_L\rangle_n| \leq \| w \|_\infty \frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq
  \sigma \sqrt{\log \frac{n}{\delta}} \left( \epsilon + \epsilon_{n,\delta} \right)
\]
For the last inequality, we used the fact that $w$ is a vector of independent subgaussian($\sigma$) random variables and hence, by union bound, with probability at least $1-\delta$, $\| w \|_\infty \leq \sigma \sqrt{\log \frac{n}{\delta}}$.

@@

Putting this together, we have that
\begin{align*}
|\langle w, h \rangle_n | &\leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|\\
|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
     | \sup_{h^L} \langle w, h^L \rangle_n | + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq   sB \sigma \sqrt{ \frac{ \log N_{[]} + \log 1/\delta}{cn}} + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq  sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}}} +
   \sigma \sqrt{ \log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}}} +
   \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
   &\leq \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log 1/\delta}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
\end{align*}

The two terms are balanced when one sets $\epsilon = \sqrt{ \frac{((sB)^2 s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$.

@@

@@

\[
|\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
\]

@@

Plugging this result into equation~\ref{eqn:first_step_inequality} and using an union bound, we get, with probability at least $1 - 2\delta$:
\begin{align}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq c sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
   + \lambda 4 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log \frac{1}{\delta}}{c n^{4/5}}}
   + \lambda 4 s B \nonumber\\   
   &\leq cB \sigma 
    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log \frac{C}{\delta}} + \lambda 4 sB
\label{eqn:second_step_inequality}
\end{align}

@@

\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
   &\leq cB^2 \sigma 
    \sqrt{ \frac{s^5 (b c_u)^{2/5}}{n^{4/5}} \log \frac{C}{\delta}}
 +\lambda 4 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
    \nonumber \\
&\leq c B^3 \sigma \sqrt{ \frac{s^5(bc_u)^{2/5}}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sB
\end{align}

@@

\begin{theorem}
\label{thm:concave_consistent}
Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq c sLb \sqrt{\frac{1}{n} \log^2 np}$.\\

Suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta} } \leq 1$.\\

@@

\textbf{Step 1.} We start from the definition of $\hat{g}_k$:
\begin{align*}
\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda \| \hat{g} \|_\infty &\leq
   \| y - \hat{f} - g^*_k \|_n^2 + \lambda \| g^* \|_\infty \\
\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda 2 Lb \\
 &\\
\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
   +\lambda 2 Lb \\
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda 2Lb
\end{align*}

Using identical analysis as Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda 2 Lb
\end{align*}

Using the uniform convergence result (lemma~\ref{lem:uniform_convergence}), we have, with probability at least $1-2\delta$:
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  c (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
  c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
 &\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
\end{align*}

Plugging in $\lambda \leq \sqrt{ \frac{1}{n} \log^2 np}$:
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
    2Lb \sqrt{\frac{1}{n} \log^2 np}\\
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
\end{align*}

@@

\begin{align*}
\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle
   + 2 \langle f_0 - f^*, g^*_k \rangle \\
 &\leq c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
    2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
 &\leq  c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
    2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
&\leq  c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
   c (Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
&\leq  c (Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
\end{align*}

@@

\textbf{Step 3.} Collecting the results from Step 1 and Step 2, we have, with probability at least $1-2\delta$:
\begin{align*}
\| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
   c (Lb)^{2.5} \sigma^{0.5} 
     \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
\end{align*}

@@

\begin{lemma}
\label{lem:uniform_convergence}
With probability at least $1-\delta$:
\begin{align*}
\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
   c B^2 \sqrt{ \frac{s^5b^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}

\end{lemma}

@@

By Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$. By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\| h_U - h_L \|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{2 \epsilon^{1/2} n}}$.

@@

$\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with upper bound $sB$. By uniform convergence, we have that, with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$):
\[
\left| \frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - 
   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
\]

Plugging this into equation~\ref{eqn:hpsi_bound} above, we have that:
\begin{align*}
& \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} } \\
 & \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
\E \psi_U(X)^2 - \E \psi_L(X)^2 + 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
\end{align*}

Using the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ result, we have:
\begin{align*}
-sB\epsilon - 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} } \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
sB\epsilon + 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} + \log \frac{1}{\delta}}{ \epsilon^{1/2} n} }
\end{align*}

@@

We have then that, with probability at least $1-\delta$,
\begin{align*}
\big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
  B^2 \sqrt{ \frac{s^5 b^{1/2} \log \frac{1}{\delta}}{n^{4/5}}}
\end{align*}

@@

\begin{align*}
| \bar{f}^* | | \bar{f}_0 | &\leq c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \\
\bar{f}^{*2} &\leq c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\end{align*}

Therefore, with probability at least $1 - 2\delta$,
\[
\|f_0 - f^*\|_n^2 - c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
    \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
\|f_0 - f^*\|_n^2 + c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\]

@@

where 
$\epsilon_{n,\delta} \equiv 
sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} = 
sB \sqrt{ \frac{sK^{**} (2sbB)^{d/2} + \log \frac{1}{\delta}}{2\epsilon^{d/2} n} }$
\end{corollary}

\begin{proof}
$|f_L(X_i) - f_U(X_i)|$ is at most $sB$. There are $N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$. The inequality follows from a direct application of union bound and Hoeffding Inequality.\\
\end{proof}
% \subsubsection{Covering Number for Lipschitz Convex Functions}

@@

%%% Local Variables: ***
%%% mode:latex ***
%%% TeX-master: "paper.tex" ***
%%% End: ***

>>>>

\begin{theorem}
\label{thm:convex_consistent}
Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq sB \sqrt{ \frac{1}{n} \log^2 np}$.

Suppose $n \geq c_1 \max(\sqrt{sB}, B)$ and $B, \sigma \geq c_2$ for some constant $c_1, c_2$.

Then, with probability at least $1-\delta$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{Cnp}{\delta}}
\end{align}
Where $c, C$ are constants, dependent on $c_1, c_2$.

@@

The middle term can be bounded with the fact that $\|f^*_k - \bar{f}^*_k \|_\infty \leq 4B$.

@@

By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.

By Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
)^{1/2} + \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$.

@@

$$
\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}
$$.
Where we assumed that condition~\ref{cond:simplify_covering_number} holds.

We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{ \frac{sK^{**}(2sbBc_u)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. 
Therefore,  
\[
|\langle w, h - h_L\rangle_n| \leq \| w \|_\infty \frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq
  \sigma \sqrt{\log \frac{n}{\delta}} \left( \epsilon + \epsilon_{n,\delta} \right)
\]
For the last inequality, we used the fact that $w$ is a vector of independent subgaussian($\sigma$) random variables and hence, by union bound, with probability at least $1-\delta$, $\| w \|_\infty \leq \sigma \sqrt{\log \frac{n}{\delta}}$.

@@

Putting this together, we have that
\begin{align*}
|\langle w, h \rangle_n | &\leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|\\
|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| &\leq 
     | \sup_{h^L} \langle w, h^L \rangle_n | + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq   sB \sigma \sqrt{ \frac{ \log N_{[]} + \log \frac{1}{\delta}}{cn}} + \sigma \sqrt{\log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq  sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{cn \epsilon^{1/2}}} +
   \sigma \sqrt{ \log \frac{n}{\delta}} (\epsilon + \epsilon_{n, \delta}) \\
   &\leq sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{cn \epsilon^{1/2}}} +
   \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} + \log \frac{1}{\delta}}{cn \epsilon^{1/2}} \log \frac{n}{\delta}} \\
   &\leq \sigma\sqrt{\log \frac{n}{\delta}} \epsilon + sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{n}{\delta}}{cn \epsilon^{1/2}}} \\
\end{align*}

The two terms are balanced when one sets $\epsilon = sB \sqrt{ \frac{(s K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$.

@@

Also, to ensure that conditions~\ref{cond:simplify_covering_number} hold, we need that $\log n \geq 2$ and $n \geq c B$ where $c$ is some constant dependent only on $K^{**}$ and $b$.

@@

\[
|\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log^2 \frac{n}{\delta}}{c n^{4/5}}}
\]

@@

Plugging this result into equation~\ref{eqn:first_step_inequality} and using an union bound, we get, with probability at least $1 - 2\delta$:
\begin{align}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq c sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log^2 \frac{n}{\delta}}{n^{4/5}}}
   + \lambda 4 s B + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq c sB \sigma \sqrt{ 
   \frac{s b^{1/2} \log^2 \frac{nC}{\delta}}{n^{4/5}}}
   + \lambda 4 s B \nonumber\\   
   &\leq c B \sigma 
    \sqrt{ \frac{s^3 b^{1/2}}{n^{4/5}} \log^2 \frac{n}{\delta}} + \lambda 4 sB
\label{eqn:second_step_inequality}
\end{align}

@@

\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
   &\leq cB^2 \sigma 
    \sqrt{ \frac{s^3 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
 +\lambda 4 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
    \nonumber \\
&\leq c B^3 \sigma \sqrt{ \frac{s^5 b^{2/5}}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 4 sB \nonumber
\end{align}
Where for the second inequality, we used the assumption that there is some large constant $c$ such that $B \geq \frac{\sigma}{c\sigma + 1}$.

@@

\begin{theorem}
\label{thm:concave_consistent}
Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq c sB \sqrt{\frac{1}{n} \log^2 np}$.\\

Suppose $n$ is large enough such that $B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta} } \leq 1$.\\

@@

\textbf{Step 1.} We start from the definition of $\hat{g}_k$:
\begin{align*}
\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda \| \hat{g} \|_\infty &\leq
   \| y - \hat{f} - g^*_k \|_n^2 + \lambda \| g^* \|_\infty \\
\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda 2B \\
 &\\
\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
   +\lambda 2 B \\
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda 2B
\end{align*}

Using identical analysis as Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda 2 B
\end{align*}

Using the uniform convergence result (lemma~\ref{lem:uniform_convergence}), we have, with probability at least $1-2\delta$:
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
  c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
 &\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
\end{align*}

Plugging in $\lambda \leq \sqrt{ \frac{1}{n} \log^2 np}$:
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c B^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
    2Lb \sqrt{\frac{1}{n} \log^2 np}\\
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c B^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
\end{align*}

@@

\begin{align*}
\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle
   + 2 \langle f_0 - f^*, g^*_k \rangle \\
 &\leq c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
    2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
 &\leq  c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
    2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
&\leq  c B^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
   c B \sqrt{B^3\sigma \sqrt{ 
                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
&\leq  cB \sqrt{B^3\sigma \sqrt{ 
                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
\end{align*}

@@

\textbf{Step 3.} Collecting the results from Step 1 and Step 2, we have, with probability at least $1-2\delta$:
\begin{align*}
\| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
   c B^{2.5} \sigma^{0.5} 
     \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
\end{align*}

@@

\begin{lemma}
\label{lem:uniform_convergence}
With probability at least $1-\delta$:
\begin{align*}
\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
   c B^2 \sqrt{ \frac{s^5b^{1/2}}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}
\end{lemma}

@@

By Corollary~\ref{cor:convexadditive_lp}, the bracketing has size at most $\log N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P)) \leq s K^{**}\left( \frac{2sbB}{\epsilon} \right)^{1/2}$. By Corollary~\ref{cor:convexbracket_ln}, we know that with probability at least $1-\delta$, we have that $\|h_U - h_L\|_{L_1(P_n)} \leq \epsilon + \epsilon_{n,\delta}$ for all pairs $(h_U, h_L)$ in the bracketing, where $\epsilon_{n,\delta} = sB \sqrt{ \frac{K^{**} (2sbB)^{1/2} \log \frac{2}{\delta}}{2 \epsilon^{1/2} n}}$.

@@

$\psi_L(X_i)^2$ and $\psi_U(X_i)^2$ are bounded random variables with upper bound $sB$. By Hoeffding's inequality and union bound, we have that, with probability at least $1-\delta$,, for all $\psi_L$ (and likewise $\psi_U$):
\[
\left| \frac{1}{n} \sum_{i=1}^n \psi_L(X_i)^2 - 
   \E \psi_L(X)^2 \right| \leq (sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
\]

Plugging this into equation~\ref{eqn:hpsi_bound} above, we have that:
\begin{align*}
& \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \\
 & \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
\E \psi_U(X)^2 - \E \psi_L(X)^2 + 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
\end{align*}

Using the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$ result, we have:
\begin{align*}
-sB\epsilon - 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
sB\epsilon + 
(sB)^2 \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
\end{align*}

@@

We have then that, with probability at least $1-\delta$,
\begin{align*}
\big| \| h \|_n^2 - \| h \|_P^2  \big| \leq
  B^2 \sqrt{ \frac{s^5 b^{1/2} \log \frac{2}{\delta}}{n^{4/5}}}
\end{align*}

@@

\begin{align*}
| \bar{f}^* | | \bar{f}_0 | &\leq c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \\
\bar{f}^{*2} &\leq c (sB)^2 \frac{1}{n} \log \frac{2}{\delta}
\end{align*}

Therefore, with probability at least $1 - 2\delta$,
\[
\|f_0 - f^*\|_n^2 - c (sB)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
    \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
\|f_0 - f^*\|_n^2 + c (sB)^2 \frac{1}{n} \log \frac{2}{\delta}
\]

@@

where 
$\epsilon_{n,\delta} \equiv 
sB \sqrt{ \frac{ \log N_{[]}(2\epsilon, \mathcal{C}^s, L_2(P)) + \log \frac{1}{\delta}}{2n}} 
= \sqrt{ \frac{ sK^{**}(sBb)^{1/2}}{2\epsilon^{1/2}n} + \frac{1}{2n} \log \frac{1}{\delta}}$
\end{corollary}

\begin{proof}
$|f_L(X_i) - f_U(X_i)|$ is at most $sB$. There are $N_{[]}(2\epsilon, \mathcal{C}^s, L_1(P))$ pairs $(f_L, f_U)$. The inequality follows from a direct application of union bound and Hoeffding Inequality.\\
\end{proof}

To make the expression in this corollary easier to work with, we derive an upper bound for $\epsilon_{n, \delta}$. Suppose 
\begin{align}
\epsilon^{1/2} \leq 2sK^{**} (sBb)^{1/2} \quad \trm{and} \quad \log \frac{1}{\delta} \geq 2. \label{cond:simplify_covering_number}
\end{align}

Then we have that
\begin{align*}
\epsilon_n \leq sB \sqrt{ \frac{ sK^{**} (sBb)^{1/2} \log \frac{1}{\delta}}{\epsilon^{1/2}n}}
\end{align*}

% \subsubsection{Covering Number for Lipschitz Convex Functions}

@@

%%% Local Variables: ***
%%% mode:latex ***
%%% TeX-master: "faithful.tex" ***
%%% End: ***
